Modeling browser-based distributed evolutionary computation systems

### 2015-03-21 modeling-volunteer-computing-gecco.tex
Further corrections
A few corrections on the fly

The world has computational resources in spades. Most of them do not
belong to you or your lab. That does not mean you cannot use it. The
problem is how.

Most theory in parallel computing has been devoted to predict and
optimize the performance in systems where the number of nodes, their
connections, and the time every one is dedicating to the computation is
%FERGU: cambiado el devoting que se repite, por dedicating 
known in advance. However, even if Big Science is not really over and
it is slated to come back, the era of
Citizen Science already started a few years ago (with SETI@home \cite{david-seti:home} and then BOINC \cite{boinc_grid04}) and it
offers a vast amount of computational resources to attract, if only
you know how. But there is a challenge: knowing, or at least having a
ballpark, of how your algorithm is going to perform in this uncertain
environment, where none of the factors is known: neither the number of
nodes, through how they are connected, to how long are they going to
be focused on doing what you want them to. That is why some effort is
needed to first understand the dynamics of the decision to participate
in an experiment that requires you to click on a link and then stay
for a while looking at the screen (or just leave it there running).

>>>>

The world has computational resources in spades. Most of them do not
belong to you or your lab. That does not mean you cannot use them. The
problem is how.

Most theory in parallel computing has been devoted to predict and
optimize the performance in systems where the number of nodes, their
connections, and the time every one is dedicating to the computation is
known in advance. However, even if Big Science is not really over and
it is slated to come back, the era of
Citizen Science already started a few years ago (with SETI@home \cite{david-seti:home} and then BOINC \cite{boinc_grid04}) and it
offers a vast amount of computational resources to be used, if only
you know how to attract them. But there is a challenge: knowing, or at least having a
ballpark, of how your algorithm is going to perform in this uncertain
environment, where none of the factors is known: neither the number of
nodes, through how they are connected, to how long are they going to
be focused on doing what you want them to. That is why some effort is
needed to first understand the dynamics of the decision to participate
in an experiment that requires you to click on a link and then stay
for a while looking at the screen (or just leave it there running).
